MacLeish

### 2016-03-25 README.Rmd
fixed type in README
added research plots

The Ada and Archibald MacLeish Field Station is a 240-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation. Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.  More information can be found at (http://www.smith.edu/ceeds/macleish.php)

@@

Weather data from 2015 is available immediately from two both the `Whately` and `Orchard` weather stations.

@@

```{r, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = macleish_layers[["buildings"]], 
              weight = 1, popup = ~ Feature) %>%
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ Name) %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2)
```

>>>>

The Ada and Archibald MacLeish Field Station is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation. Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.  More information can be found at (http://www.smith.edu/ceeds/macleish.php)

@@

Weather data from 2015 is available immediately from both the `Whately` and `Orchard` weather stations.

@@

```{r, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = macleish_layers[["boundary"]], 
              weight = 1, fillOpacity = 0.1) %>%
  addPolygons(data = macleish_layers[["buildings"]], 
              weight = 1, popup = ~ Feature) %>%
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ Name) %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2)
```
